Titeln på avhandlingens språk

### 2023-05-11 body/acks.tex
acks

Furthermore, I would like to extend my sincere thanks to Prof. Sandra Céspedes, of Universidad de Chile and Concordia University, for her guidance and urging to embark on this journey towards a Ph.D., and for always being willing to offer help and advice.
Likewise, I'd like to thank Prof. Javier Bustos, of Universidad de Chile and NIC Chile Research Labs, for giving me the opportunity many years ago to first get into distributed systems research.
Also, I'd like to extend my gratitude to Prof. José Miguel Piquer, of Universidad de Chile, for taking me as his ``long-distance'' teaching assistant and allowing me to give back to my \emph{alma mater} from across the ocean.

@@

I would also like to thank all of my friends who have made this long, ardous journey more amenable.
I would particularly like to thank everyone I met through Tartan Salsa, including, but not limited to, Andresa, Jennifer, Alyson, Kuai-Kuai, Carmen, Moataz and Nora, Eric, and many others.
They made Pittsburgh feel like home, even before I finally moved there permanently in 2022.
I also want to thank Ann-Charlotte in Stockholm, for always being so kind, so considerate, and so much fun to hang with.
Further, I am deeply grateful for my friends in Chile who have remained a source of support, even though we only get to see each other once a year when I visit.
This includes, but is not limited to, Juan Pablo, Fernanda, Diego, Camila, George, Patricio, Kevin, Pablo, and many others.
Yet another special mention goes to Diego's family, who have always treated me as one of their own.

>>>>

Furthermore, I would like to extend my sincere thanks to Prof. Sandra Céspedes, of Universidad de Chile and Concordia University, for her guidance and urging to embark on this journey towards a Ph.D., and for always being willing to offer help and advice.
Likewise, I'd like to thank Prof. Javier Bustos, of Universidad de Chile and NIC Chile Research Labs, for giving me the opportunity many years ago to first get into distributed systems research.
Also, I'd like to extend my gratitude to Prof. José Miguel Piquer, of Universidad de Chile, for taking me as his ``long-distance'' teaching assistant and allowing me to give back to my \emph{alma mater} from across the ocean.
A very special thanks goes out to Prof. Jérémy Barbay of Universidad de Chile and Universidad de Concepción, for being a mentor and a friend since the day I took his course on Android programming while an undergraduate student.
I am deeply appreciative of the fact that although our interactions have been sporadic at best these last few years, I can always reach out to him for help and advice when I need it.

@@

I would also like to thank all of my friends who have made this long, ardous journey more amenable.
I would particularly like to thank everyone I met through Tartan Salsa, including, but not limited to, Andresa, Jennifer, Alyson, Kuai-Kuai, Carmen, Moataz and Nora, Eric, and many others.
They made Pittsburgh feel like home, even before I finally moved there permanently in 2022.
I also want to thank Ann-Charlotte in Stockholm, for always being so kind, so considerate, and so much fun to be around.
Further, I am deeply grateful to my friends in Chile who have remained a source of support, even though we only get to see each other once a year when I visit.
This includes, but is not limited to, Juan Pablo, Fernanda, Diego, Camila, George, Patricio, Kevin, Pablo, and many others.
Yet another special mention goes to Diego's family, who have always treated me as one of their own.
